---
title: "PUBG Strategies"
output: pdf_document
---

## Install libraries
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(reshape2)
library(tidyr)
library(dplyr)
library(scales)
source('util.R')
```

## Load data
```{r}
#setwd("/Users/alex/Desktop/AMS204-FinalProject")
PUBG_full <- read.csv("data/train_V2.csv")
#PUBG_test <- read.csv("data/test_V2.csv")
```

## Seperating dataset by match type's covariants and response
```{r}
# Solo dataset
solo <- preprocess(PUBG_full, 'solo')
solo_org_large_cov <- solo$first
solo_org_small_cov <- solo$second
solo_org_large_resp <- solo$third
solo_org_small_resp <- solo$fourth
solo_org_large_full <- data.frame(solo_org_large_cov, solo_org_large_resp)
solo_org_small_full <- data.frame(solo_org_large_cov, solo_org_large_resp)

# Solo-Fpp dataset
solo_fpp <- preprocess(PUBG_full, 'solo-fpp')
solo_fpp_large_df <- solo_fpp$first
solo_fpp_small_df <- solo_fpp$second
solo_fpp_large_resp <- solo_fpp$third
solo_fpp_small_resp <- solo_fpp$fourth
solo_fpp_org_large_full <- data.frame(solo_fpp_org_large_cov, solo_fpp_org_large_resp)
solo_fpp_org_small_full <- data.frame(solo_fpp_org_large_cov, solo_fpp_org_large_resp)

# Duo dataset
duo <- preprocess(PUBG_full, 'duo')
duo_large_df <- duo$first
duo_small_df <- duo$second
duo_large_resp <- duo$third
duo_small_resp <- duo$fourth
duo_org_large_full <- data.frame(duo_org_large_cov, duo_org_large_resp)
duo_org_small_full <- data.frame(duo_org_large_cov, duo_org_large_resp)

# Duo-Fpp dataset
duo_fpp <- preprocess(PUBG_full, 'duo-fpp')
duo_fpp_large_df <- duo_fpp$first
duo_fpp_small_df <- duo_fpp$second
duo_fpp_large_resp <- duo_fpp$third
duo_fpp_small_resp <- duo_fpp$fourth
duo_fpp_org_large_full <- data.frame(duo_fpp_org_large_cov, duo_fpp_org_large_resp)
duo_fpp_org_small_full <- data.frame(duo_fpp_org_large_cov, duo_fpp_org_large_resp)

# Squad dataset
squad <- preprocess(PUBG_full, 'squad')
squad_large_df <- squad$first
squad_small_df <- squad$second
squad_large_resp <- squad$third
squad_small_resp <- squad$fourth
squad_org_large_full <- data.frame(squad_org_large_cov, squad_org_large_resp)
squad_org_small_full <- data.frame(squad_org_large_cov, squad_org_large_resp)

# Squad-Fpp dataset
squad_fpp <- preprocess(PUBG_full, 'squad-fpp')
squad_fpp_large_df <- squad_fpp$first
squad_fpp_small_df <- squad_fpp$second
squad_fpp_large_resp <- squad_fpp$third
squad_fpp_small_resp <- squad_fpp$fourth
squad_fpp_org_large_full <- data.frame(squad_fpp_org_large_cov, squad_fpp_org_large_resp)
squad_fpp_org_small_full <- data.frame(squad_fpp_org_large_cov, squad_fpp_org_large_resp)
```

```{r}
### Solo

# Splitting dataset into clusters
solo_org_large_full <- append_clustering_feature(solo_org_large_cov, solo_org_large_full)
solo_org_large <- split_by_the_four_clusters(solo_org_large_full)
cluster_1_solo_org_large <- data.frame(solo_org_large$first) 
cluster_2_solo_org_large <- data.frame(solo_org_large$second) 
cluster_3_solo_org_large <- data.frame(solo_org_large$third) 
cluster_4_solo_org_large <- data.frame(solo_org_large$fourth)

# Splitting the clusters into covariants and response
omit_response <- !names(solo_org_large_full) %in% c("winPlacePerc") 

cluster_1_solo_org_large_cov <- cluster_1_solo_org_large[, omit_response]
cluster_1_solo_org_large_resp <- cluster_1_solo_org_large$winPlacePerc
cluster_2_solo_org_large_cov <- cluster_2_solo_org_large[, omit_response]
cluster_2_solo_org_large_resp <- cluster_2_solo_org_large$winPlacePerc
cluster_3_solo_org_large_cov <- cluster_3_solo_org_large[, omit_response]
cluster_3_solo_org_large_resp <- cluster_3_solo_org_large$winPlacePerc
cluster_4_solo_org_large_cov <- cluster_4_solo_org_large[, omit_response]
cluster_4_solo_org_large_resp <- cluster_4_solo_org_large$winPlacePerc
```

```{r}
# Solo Fpp
```

```{r}
# Duo
```

```{r}
# Duo Fpp
```

## Transform the response of the data for linear regression
```{r}
# TODO Last once normal linear regression is running
```

## Linear Regression (run model and assess the fit)
```{r}

```

## Add >.9 Threshold Feature to a new data frame 
```{r}

```

## Logistic Regression (run model and check classification percent correct)
```{r}

```

## Extra Add ROC Curves and play with threshold of log regression if we have time