---
title: "PUBG Strategies"
output: pdf_document
---

## Install libraries
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(reshape2)
library(tidyr)
library(dplyr)
library(scales)
library("plyr")
source('util.R')
```

## Load  and Shuffle Data
```{r}
#setwd("/Users/alex/Desktop/PUBG_Project")
set.seed(57483)
PUBG_full <- read.csv("data/train_V2.csv")
PUBG_full <- PUBG_full[sample(nrow(PUBG_full)),]
```

## Seperating dataset by match type's covariates and response
```{r}
### Solo first person perspective dataset
solo <- preprocess(PUBG_full, 'solo')
solo_org_small_cov <- solo$first
solo_org_small_resp <- solo$second
solo_org_small_full <- data.frame(solo_org_small_cov, solo_org_small_resp)
colnames(solo_org_small_full)[19] <- 'winPlacePerc'

### Solo first person perspective dataset
solo_fpp <- preprocess(PUBG_full, 'solo-fpp')
solo_fpp_small_cov <- solo_fpp$first
solo_fpp_small_resp <- solo_fpp$second
solo_fpp_small_full <- data.frame(solo_fpp_small_cov, solo_fpp_small_resp)
colnames(solo_fpp_small_full)[19] <- 'winPlacePerc'
```

## Data split into train and test set
```{r}
split = 0.9

### Solo orginal perspective
len_org = length(solo_org_small_cov$assists)

# Covariates train, test dataset split
solo_org_small_cov_set <- train_test_split(solo_org_small_cov, split, len_org)
train_solo_org_small_cov <- solo_org_small_cov_set$train
test_solo_org_small_cov <- solo_org_small_cov_set$test

# Response train, test dataset split
solo_org_small_resp_set <- train_test_split_resp(solo_org_small_resp, split, len_org)
train_solo_org_small_resp <- solo_org_small_resp_set$train
test_solo_org_small_resp <- solo_org_small_resp_set$test
```

```{r}
### Solo first person perspective
len_fpp = length(solo_fpp_small_cov$assists)

# Covariates train, test dataset split
solo_fpp_small_cov_set <- train_test_split(solo_fpp_small_cov, 0.9, len_fpp)
train_solo_fpp_small_cov <- solo_fpp_small_cov_set$train
test_solo_fpp_small_cov <- solo_fpp_small_cov_set$test

# Response train, test dataset split
solo_fpp_small_resp_set <- train_test_split_resp(solo_fpp_small_resp, 0.9, len_fpp)
train_solo_fpp_small_resp <- solo_fpp_small_resp_set$train
test_solo_fpp_small_resp <- solo_fpp_small_resp_set$test
```

## K-means clustering
```{r}
### Solo orginal perspective clustering
# Splitting dataset into clusters
solo_org_small_full <- append_clustering_feature(solo_org_small_cov, solo_org_small_full)
solo_org_small <- split_by_the_four_clusters(solo_org_small_full)
cluster_1_solo_org_small <- data.frame(solo_org_small$first) 
cluster_2_solo_org_small <- data.frame(solo_org_small$second) 
cluster_3_solo_org_small <- data.frame(solo_org_small$third) 
cluster_4_solo_org_small <- data.frame(solo_org_small$fourth)

# Splitting the clusters into covariants and response
omit_response <- !names(solo_org_small_full) %in% c("winPlacePerc") 

len_org_clus_1 = length(cluster_1_solo_org_small$assists)
len_org_clus_2 = length(cluster_2_solo_org_small$assists)
len_org_clus_3 = length(cluster_3_solo_org_small$assists)
len_org_clus_4 = length(cluster_4_solo_org_small$assists)

cluster_1_solo_org_small_cov <- cluster_1_solo_org_small[, omit_response]
cluster_1_solo_org_small_cov_set <- train_test_split(cluster_1_solo_org_small_cov, split, len_org_clus_1)
c1_train_solo_org_small_cov <- cluster_1_solo_org_small_cov_set$train
c1_test_solo_org_small_cov <- cluster_1_solo_org_small_cov_set$test

cluster_1_solo_org_small_resp <- cluster_1_solo_org_small$winPlacePerc
cluster_1_solo_org_small_resp_set <- train_test_split_resp(cluster_1_solo_org_small_resp, split, len_org_clus_1)
c1_train_solo_org_small_resp <- cluster_1_solo_org_small_resp_set$train
c1_test_solo_org_small_resp <- cluster_1_solo_org_small_resp_set$test

cluster_2_solo_org_small_cov <- cluster_2_solo_org_small[, omit_response]
cluster_2_solo_org_small_cov_set <- train_test_split(cluster_2_solo_org_small_cov, split, len_org_clus_2)
c2_train_solo_org_small_cov <- cluster_2_solo_org_small_cov_set$train
c2_test_solo_org_small_cov <- cluster_2_solo_org_small_cov_set$test

cluster_2_solo_org_small_resp <- cluster_2_solo_org_small$winPlacePerc
cluster_2_solo_org_small_resp_set <- train_test_split_resp(cluster_2_solo_org_small_resp, split, len_org_clus_2)
c2_train_solo_org_small_resp <- cluster_2_solo_org_small_resp_set$train
c2_test_solo_org_small_resp <- cluster_2_solo_org_small_resp_set$test

cluster_3_solo_org_small_cov <- cluster_3_solo_org_small[, omit_response]
cluster_3_solo_org_small_cov_set <- train_test_split(cluster_3_solo_org_small_cov, split, len_org_clus_3)
c3_train_solo_org_small_cov <- cluster_3_solo_org_small_cov_set$train
c3_test_solo_org_small_cov <- cluster_3_solo_org_small_cov_set$test

cluster_3_solo_org_small_resp <- cluster_3_solo_org_small$winPlacePerc
cluster_3_solo_org_small_resp_set <- train_test_split_resp(cluster_3_solo_org_small_resp, split, len_org_clus_3)
c3_train_solo_org_small_resp <- cluster_3_solo_org_small_resp_set$train
c3_test_solo_org_small_resp <- cluster_3_solo_org_small_resp_set$test

cluster_4_solo_org_small_cov <- cluster_4_solo_org_small[, omit_response]
cluster_4_solo_org_small_cov_set <- train_test_split(cluster_4_solo_org_small_cov, split, len_org_clus_4)
c4_train_solo_org_small_cov <- cluster_4_solo_org_small_cov_set$train
c4_test_solo_org_small_cov <- cluster_4_solo_org_small_cov_set$test

cluster_4_solo_org_small_resp <- cluster_4_solo_org_small$winPlacePerc
cluster_4_solo_org_small_resp_set <- train_test_split_resp(cluster_4_solo_org_small_resp, split, len_org_clus_4)
c4_train_solo_org_small_resp <- cluster_4_solo_org_small_resp_set$train
c4_test_solo_org_small_resp <- cluster_4_solo_org_small_resp_set$test

# cluster_2_solo_org_small_cov <- cluster_2_solo_org_small[, omit_response]
# cluster_2_solo_org_small_resp <- cluster_2_solo_org_small$winPlacePerc
# cluster_3_solo_org_small_cov <- cluster_3_solo_org_small[, omit_response]
# cluster_3_solo_org_small_resp <- cluster_3_solo_org_small$winPlacePerc
# cluster_4_solo_org_small_cov <- cluster_4_solo_org_small[, omit_response]
# cluster_4_solo_org_small_resp <- cluster_4_solo_org_small$winPlacePerc
```

```{r}
### Solo first person perspective clustering
# Splitting dataset into clusters
solo_fpp_small_full <- append_clustering_feature(solo_fpp_small_cov, solo_fpp_small_full)
solo_fpp_small <- split_by_the_four_clusters(solo_fpp_small_full)
cluster_1_solo_fpp_small <- data.frame(solo_fpp_small$first) 
cluster_2_solo_fpp_small <- data.frame(solo_fpp_small$second) 
cluster_3_solo_fpp_small <- data.frame(solo_fpp_small$third) 
cluster_4_solo_fpp_small <- data.frame(solo_fpp_small$fourth)

# Splitting the clusters into covariants and response
omit_response <- !names(solo_fpp_small_full) %in% c("winPlacePerc") 

len_fpp_clus_1 = length(cluster_1_solo_fpp_small$assists)
len_fpp_clus_2 = length(cluster_2_solo_fpp_small$assists)
len_fpp_clus_3 = length(cluster_3_solo_fpp_small$assists)
len_fpp_clus_4 = length(cluster_4_solo_fpp_small$assists)

cluster_1_solo_fpp_small_cov <- cluster_1_solo_fpp_small[, omit_response]
cluster_1_solo_fpp_small_cov_set <- train_test_split(cluster_1_solo_fpp_small_cov, split, len_fpp_clus_1)
c1_train_solo_fpp_small_cov <- cluster_1_solo_fpp_small_cov_set$train
c1_test_solo_fpp_small_cov <- cluster_1_solo_fpp_small_cov_set$test

cluster_1_solo_fpp_small_resp <- cluster_1_solo_fpp_small$winPlacePerc
cluster_1_solo_fpp_small_resp_set <- train_test_split_resp(cluster_1_solo_fpp_small_resp, split, len_fpp_clus_1)
c1_train_solo_fpp_small_resp <- cluster_1_solo_fpp_small_resp_set$train
c1_test_solo_fpp_small_resp <- cluster_1_solo_fpp_small_resp_set$test

cluster_2_solo_fpp_small_cov <- cluster_2_solo_fpp_small[, omit_response]
cluster_2_solo_fpp_small_cov_set <- train_test_split(cluster_2_solo_fpp_small_cov, split, len_fpp_clus_2)
c2_train_solo_fpp_small_cov <- cluster_2_solo_fpp_small_cov_set$train
c2_test_solo_fpp_small_cov <- cluster_2_solo_fpp_small_cov_set$test

cluster_2_solo_fpp_small_resp <- cluster_2_solo_fpp_small$winPlacePerc
cluster_2_solo_fpp_small_resp_set <- train_test_split_resp(cluster_2_solo_fpp_small_resp, split, len_fpp_clus_2)
c2_train_solo_fpp_small_resp <- cluster_2_solo_fpp_small_resp_set$train
c2_test_solo_fpp_small_resp <- cluster_2_solo_fpp_small_resp_set$test

cluster_3_solo_fpp_small_cov <- cluster_3_solo_fpp_small[, omit_response]
cluster_3_solo_fpp_small_cov_set <- train_test_split(cluster_3_solo_fpp_small_cov, split, len_fpp_clus_3)
c3_train_solo_fpp_small_cov <- cluster_3_solo_fpp_small_cov_set$train
c3_test_solo_fpp_small_cov <- cluster_3_solo_fpp_small_cov_set$test

cluster_3_solo_fpp_small_resp <- cluster_3_solo_fpp_small$winPlacePerc
cluster_3_solo_fpp_small_resp_set <- train_test_split_resp(cluster_3_solo_fpp_small_resp, split, len_fpp_clus_3)
c3_train_solo_fpp_small_resp <- cluster_3_solo_fpp_small_resp_set$train
c3_test_solo_fpp_small_resp <- cluster_3_solo_fpp_small_resp_set$test

cluster_4_solo_fpp_small_cov <- cluster_4_solo_fpp_small[, omit_response]
cluster_4_solo_fpp_small_cov_set <- train_test_split(cluster_4_solo_fpp_small_cov, split, len_fpp_clus_4)
c4_train_solo_fpp_small_cov <- cluster_4_solo_fpp_small_cov_set$train
c4_test_solo_fpp_small_cov <- cluster_4_solo_fpp_small_cov_set$test

cluster_4_solo_fpp_small_resp <- cluster_4_solo_fpp_small$winPlacePerc
cluster_4_solo_fpp_small_resp_set <- train_test_split_resp(cluster_4_solo_fpp_small_resp, split, len_fpp_clus_4)
c4_train_solo_fpp_small_resp <- cluster_4_solo_fpp_small_resp_set$train
c4_test_solo_fpp_small_resp <- cluster_4_solo_fpp_small_resp_set$test

# cluster_1_solo_fpp_small_cov <- cluster_1_solo_fpp_small[, omit_response]
# cluster_1_solo_fpp_small_resp <- cluster_1_solo_fpp_small$winPlacePerc
# cluster_2_solo_fpp_small_cov <- cluster_2_solo_fpp_small[, omit_response]
# cluster_2_solo_fpp_small_resp <- cluster_2_solo_fpp_small$winPlacePerc
# cluster_3_solo_fpp_small_cov <- cluster_3_solo_fpp_small[, omit_response]
# cluster_3_solo_fpp_small_resp <- cluster_3_solo_fpp_small$winPlacePerc
# cluster_4_solo_fpp_small_cov <- cluster_4_solo_fpp_small[, omit_response]
# cluster_4_solo_fpp_small_resp <- cluster_4_solo_fpp_small$winPlacePerc
```

## SMALLER MODEL - SKIP FOR NOW - Data split into train and test set
```{r}
# keep_fields <- c("damageDealt", "kills", "rideDistance", "swimDistance", "walkDistance", "int_dist")
# 
# ### Solo orginal perspective
# # Data fields fine tuning
# int_dist <- solo_org_small_cov$rideDistance / (solo_org_small_cov$rideDistance + solo_org_small_cov$walkDistance)
# new_solo_org_small_cov <- data.frame(solo_org_small_cov, int_dist)
# solo_org_small_cov_sub <- new_solo_org_small_cov[ , (names(new_solo_org_small_cov) %in% keep_fields)]
# 
# len_org = length(solo_org_small_cov$assists)
# # Covariates train, test dataset split
# solo_org_small_cov_set <- train_test_split(solo_org_small_cov_sub, 0.9, len_org)
# train_solo_org_small_cov <- solo_org_small_cov_set$train
# test_solo_org_small_cov <- solo_org_small_cov_set$test
# 
# # Response train, test dataset split
# solo_org_small_resp_set <- train_test_split_resp(solo_org_small_resp, 0.9, len_org)
# train_solo_org_small_resp <- solo_org_small_resp_set$train
# test_solo_org_small_resp <- solo_org_small_resp_set$test
```

```{r}
# ### Solo first person perspective
# # Data fields fine tuning
# int_dist <- solo_fpp_small_cov$rideDistance / (solo_fpp_small_cov$rideDistance + solo_fpp_small_cov$walkDistance)
# new_solo_fpp_small_cov <- data.frame(solo_fpp_small_cov, int_dist)
# solo_fpp_small_cov_sub <- new_solo_fpp_small_cov[ , (names(new_solo_fpp_small_cov) %in% keep_fields)]
# 
# len_fpp = length(solo_fpp_small_cov$assists)
# # Covariates train, test dataset split
# solo_fpp_small_cov_set <- train_test_split(solo_fpp_small_cov_sub, 0.9, len_fpp)
# train_solo_fpp_small_cov <- solo_fpp_small_cov_set$train
# test_solo_fpp_small_cov <- solo_fpp_small_cov_set$test
# 
# # Response train, test dataset split
# solo_fpp_small_resp_set <- train_test_split_resp(solo_fpp_small_resp, 0.9, len_fpp)
# train_solo_fpp_small_resp <- solo_fpp_small_resp_set$train
# test_solo_fpp_small_resp <- solo_fpp_small_resp_set$test
```

## Logistic Regression SKIP THIS _ COMMENTED OUT
```{r}
### Solo orginal perspective
# OG
#acc_thresh <- test_solo_org_small_resp >= 0.9
#solo_org_logit <- logistic(train_solo_org_small_cov, train_solo_org_small_resp)
#A_acc_solo_org <- accuracy(solo_org_logit$model, train_solo_org_small_cov, solo_org_logit$thresh)

#A_acc_solo_org_test <- accuracy(solo_org_logit$model, test_solo_org_small_cov, acc_thresh)
```

## Logistic Regression 
```{r}
### Solo first person perspective
# OG Full
solo_org_logit<- logistic(train_solo_org_small_cov, train_solo_org_small_resp)
acc_org_thresh <- test_solo_org_small_resp >= 0.9
acc_solo_org_test <- accuracy(solo_org_logit$model, test_solo_org_small_cov, acc_org_thresh)

# Cluster
c1_solo_org_logit<- logistic(c1_train_solo_org_small_cov, c1_train_solo_org_small_resp)
c1_acc_org_thresh <- test_solo_org_small_resp >= 0.9
acc_c1_solo_org <- accuracy(c1_solo_org_logit$model, c1_test_solo_org_small_cov, c1_acc_org_thresh)

c2_solo_org_logit<- logistic(c2_train_solo_org_small_cov, c2_train_solo_org_small_resp)
c2_acc_org_thresh <- test_solo_org_small_resp >= 0.9
acc_c2_solo_org <- accuracy(c2_solo_org_logit$model, c2_test_solo_org_small_cov, c2_acc_org_thresh)

c3_solo_org_logit<- logistic(c3_train_solo_org_small_cov, c3_train_solo_org_small_resp)
c3_acc_org_thresh <- test_solo_org_small_resp >= 0.9
acc_c3_solo_org <- accuracy(c3_solo_org_logit$model, c3_test_solo_org_small_cov, c3_acc_org_thresh)

c4_solo_org_logit<- logistic(c4_train_solo_org_small_cov, c4_train_solo_org_small_resp)
c4_acc_org_thresh <- test_solo_org_small_resp >= 0.9
acc_c4_solo_org <- accuracy(c4_solo_org_logit$model, c4_test_solo_org_small_cov, c4_acc_org_thresh)

n1_combined <- acc_c1_solo_org$n1 + acc_c2_solo_org$n1 + acc_c3_solo_org$n1 + acc_c4_solo_org$n1
n2_combined <- acc_c1_solo_org$n2 + acc_c2_solo_org$n2 + acc_c3_solo_org$n2 + acc_c4_solo_org$n2
n3_combined <- acc_c1_solo_org$n3 + acc_c2_solo_org$n3 + acc_c3_solo_org$n3 + acc_c4_solo_org$n3
n4_combined <- acc_c1_solo_org$n4 + acc_c2_solo_org$n4 + acc_c3_solo_org$n4 + acc_c4_solo_org$n4
n_total <- n1_combined + n2_combined + n3_combined + n4_combined
  
p1 <- n1_combined / n_total
p2 <- n2_combined / n_total
p3 <- n3_combined / n_total
p4 <- n4_combined / n_total
org_acc <- p1 + p4
cat("\ncluster accuracy", org_acc)
```

```{r}
### Solo first person perspective
# OG Full
solo_fpp_logit<- logistic(train_solo_fpp_small_cov, train_solo_fpp_small_resp)
acc_fpp_thresh <- test_solo_fpp_small_resp >= 0.9
acc_solo_fpp_test <- accuracy(solo_fpp_logit$model, test_solo_fpp_small_cov, acc_fpp_thresh)

# Cluster
c1_solo_fpp_logit<- logistic(c1_train_solo_fpp_small_cov, c1_train_solo_fpp_small_resp)
c1_acc_fpp_thresh <- test_solo_fpp_small_resp >= 0.9
acc_c1_solo_fpp <- accuracy(c1_solo_fpp_logit$model, c1_test_solo_fpp_small_cov, c1_acc_fpp_thresh)

c2_solo_fpp_logit<- logistic(c2_train_solo_fpp_small_cov, c2_train_solo_fpp_small_resp)
c2_acc_fpp_thresh <- test_solo_fpp_small_resp >= 0.9
acc_c2_solo_fpp <- accuracy(c2_solo_fpp_logit$model, c2_test_solo_fpp_small_cov, c2_acc_fpp_thresh)

c3_solo_fpp_logit<- logistic(c3_train_solo_fpp_small_cov, c3_train_solo_fpp_small_resp)
c3_acc_fpp_thresh <- test_solo_fpp_small_resp >= 0.9
acc_c3_solo_fpp <- accuracy(c3_solo_fpp_logit$model, c3_test_solo_fpp_small_cov, c3_acc_fpp_thresh)

c4_solo_fpp_logit<- logistic(c4_train_solo_fpp_small_cov, c4_train_solo_fpp_small_resp)
c4_acc_fpp_thresh <- test_solo_fpp_small_resp >= 0.9
acc_c4_solo_fpp <- accuracy(c4_solo_fpp_logit$model, c4_test_solo_fpp_small_cov, c4_acc_fpp_thresh)

n1_combined <- acc_c1_solo_fpp$n1 + acc_c2_solo_fpp$n1 + acc_c3_solo_fpp$n1 + acc_c4_solo_fpp$n1
n2_combined <- acc_c1_solo_fpp$n2 + acc_c2_solo_fpp$n2 + acc_c3_solo_fpp$n2 + acc_c4_solo_fpp$n2
n3_combined <- acc_c1_solo_fpp$n3 + acc_c2_solo_fpp$n3 + acc_c3_solo_fpp$n3 + acc_c4_solo_fpp$n3
n4_combined <- acc_c1_solo_fpp$n4 + acc_c2_solo_fpp$n4 + acc_c3_solo_fpp$n4 + acc_c4_solo_fpp$n4
n_total <- n1_combined + n2_combined + n3_combined + n4_combined
  
p1 <- n1_combined / n_total
p2 <- n2_combined / n_total
p3 <- n3_combined / n_total
p4 <- n4_combined / n_total
fpp_acc <- p1 + p4
cat("\ncluster accuracy", fpp_acc)
```

## Analyzing the Clusters 

### Infer the different strategies/groups that each cluster represents

```{r}
org_good_perf <- solo_org_small_resp >= .9
solo_org_cluster_df <- data.frame(solo_org_small_full, org_good_perf)
org_id <- 1:length(solo_org_cluster_df$assists)
solo_org_cluster_ids_df <- data.frame(org_id,solo_org_cluster_df)
solo_org_cluster_ids_df <- solo_org_cluster_ids_df[, !(names(solo_org_cluster_ids_df) %in% c("winPlacePerc"))]
names(solo_org_cluster_ids_df)
mdata <- melt(solo_org_cluster_ids_df, id.vars = c("org_id"))
org_cluster_pivot <- dcast(mdata, solo_org_cluster_ids_df$cluster~variable, fun.aggregate = mean)
org_cluster_freqs <- table(solo_org_cluster_df$cluster)
org_cluster_freqs_normed <- table(solo_org_cluster_df$cluster) / sum(table(solo_org_cluster_df$cluster))
org_cluster_pivot <- data.frame(org_cluster_pivot, org_cluster_freqs)
org_cluster_pivot <- data.frame(org_cluster_pivot, org_cluster_freqs_normed)
org_cluster_pivot
# Now we will

no_noobs_org_cluster_pivot <- org_cluster_pivot[-c(3),]
no_noobs_org_cluster_pivot
# Just look at Data Frame and Subset by Damage Dealt, kills, ride dist, swim dist, walk dist
# 
#scale(no_noobs_cluster_pivot)

```


```{r}
fpp_good_perf <- solo_fpp_small_resp >= .9
solo_fpp_cluster_df <- data.frame(solo_fpp_small_full, fpp_good_perf)
fpp_id <- 1:length(solo_fpp_cluster_df$assists)
solo_fpp_cluster_ids_df <- data.frame(fpp_id,solo_fpp_cluster_df)
solo_fpp_cluster_ids_df <- solo_fpp_cluster_ids_df[, !(names(solo_fpp_cluster_ids_df) %in% c("winPlacePerc"))]
names(solo_fpp_cluster_ids_df)
mdata <- melt(solo_fpp_cluster_ids_df, id.vars = c("fpp_id"))
fpp_cluster_pivot <- dcast(mdata, solo_fpp_cluster_ids_df$cluster~variable, fun.aggregate = mean)
fpp_cluster_freqs <- table(solo_fpp_cluster_df$cluster)
fpp_cluster_freqs_normed <- table(solo_fpp_cluster_df$cluster) / sum(table(solo_fpp_cluster_df$cluster))
fpp_cluster_pivot <- data.frame(fpp_cluster_pivot, fpp_cluster_freqs)
fpp_cluster_pivot <- data.frame(fpp_cluster_pivot, fpp_cluster_freqs_normed)
fpp_cluster_pivot

# Now we will

no_noobs_fpp_cluster_pivot <- fpp_cluster_pivot[-c(3),]
no_noobs_fpp_cluster_pivot
```


### Make Graph Showing How Clustering Goodness Changes Over Time 

Setting same seed as used in clustering functions to show how value changes with different clusters

```{r}
set.seed(34529078)
```


## Analyzing the Logistic Regression

### Make 4x4 table (could be in google slides) showing the different types of errors (Type 1 False Positive: Predict 1 is actually 0) (Type 2 False Negative: Predict 0 is actually 1), as well as the different types of correct estimates